plotly charts for sensitivity iteractive explorer html

### 2025-04-10 report_plotlyCharts.Rmd
release candidate - revision 1

@@

  g[["Carbon Price"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    geom_line(data=ETS_price,aes(x=Date, y=Price),size=0.5, color = "#000000") +
    scale_x_date(date_labels = "%Y") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    #ylab("€/t CO2") +
    theme(legend.spacing.y = unit(0.5, "lines")) + 
    theme(legend.position = "none")

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE") %>%
    mutate(value = round(value,2))

  h <- hist %>% filter(model == "IEA", region == "EU27", variable == "FE", period >= 2005) %>% drop_na(value) %>% filter(value != 0) %>%
    mutate(value = round(value,2))

@@

@@

>>>>

# df_beforeFilter <- df_beforeFilter %>%
#   filter(tgt2030 != 59)
# df <- df %>%
#   filter(tgt2030 != 59)

@@

  g[["Carbon Price"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=value,group = scenario)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 0.5, aes(linetype=tgt2030, color = scenario)) +
    geom_point(size = 3, aes(shape = lim, fill = scenario)) +
    geom_line(data=ETS_price,aes(x=Date, y=Price),linewidth=0.5, color = "#000000") +
    scale_x_date(date_labels = "%Y") +
    scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) + 
    scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) + 
    scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) +
    scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) +
    theme_doubleColumn() +
    theme(strip.text.y = element_blank()) +
    #guides(fill = guide_legend(nrow = 2, byrow = T)) +
    theme(legend.text=element_text(size=theme.single.text.size)) +
    theme(legend.key.height = unit(0.7, "cm"),
          legend.key.width = unit(2,"cm")) +
    theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") + 
    #theme(legend.key.width = unit(2,"cm")) +
    #ylab("€/t CO2") +
    theme(legend.spacing.y = unit(0.5, "lines")) + 
    theme(legend.position = "none")

@@

  plotData <- df_beforeFilter %>% 
    filter(region == "EU27", period %in% c(2020:2050), tgt2030 %in% tgt2030Scen, variable == "FE|w/o Non-energy Use w/o Bunkers") %>%
    mutate(value = round(value,2))

  #h <- hist %>% filter(model == "IEA", region == "EU27", variable == "FE", period >= 2005) %>% drop_na(value) %>% filter(value != 0) %>%
  #  mutate(value = round(value,2))

  h <- addHist$FE_eurostat %>%
    mutate(value = round(as.numeric(value),2),
           scenario = "historical",
           model = "Eurostat")

  factor <- h %>% filter(period %in% c(2018:2022)) %>% summarize (value = mean(value)) %>% pull(value) / plotData %>% filter(period == 2020, scenario == "Nzero_57_bio7p5") %>% pull(value)

  plotData <- plotData %>% mutate(value = factor*value)

@@

  g[["finalEnergy"]][["plotly"]]

@@

<!-- # Emission reduction -->

<!-- ```{r chart_emissions, echo=FALSE, include = FALSE} -->

<!--   h <- refEmi %>% filter(variable == "Emissions with LULUCF and with international transport", region == "EU27", pollutant == "All greenhouse gases - (CO2 equivalent)") %>% ungroup() %>% select(region,variable,period,value) %>% -->
<!--     mutate(scenario = "historical") %>% -->
<!--     mutate(value = round(value,2)) -->

<!--   plotData <- df_beforeFilter %>%  -->
<!--     filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>% -->
<!--     calc_addVariable( "`emiIntTrnsp`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr") %>% -->
<!--     calc_addVariable( "`emiIntraEU`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr") %>% -->
<!--     filter(variable %in% c("emiIntTrnsp","emiIntraEU")) %>% -->
<!--     pivot_wider(names_from = variable, values_from = value) %>% -->
<!--     mutate(ref_emiIntTrnsp = tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference), -->
<!--            ref_emiIntraEU = tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)) %>% -->
<!--     mutate(red_emiIntTrnsp = emiIntTrnsp/ref_emiIntTrnsp, -->
<!--            red_emiIntraEU = emiIntraEU/ref_emiIntraEU) %>% -->
<!--     mutate(value = emiIntTrnsp, -->
<!--            reduction = ifelse(period >= 2045, red_emiIntTrnsp, red_emiIntraEU)) %>% -->
<!--     mutate(text = paste0("Emissions: ", round(value), " Mt CO2/yr", "\nReduction: ", round(1-reduction,3)*100, "%", "\nPeriod: ", period, "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim)) %>% -->
<!--     mutate(value = round(value,2)) -->

<!--   g[["Emission reduction"]][["ggplot"]] <- ggplot(plotData,aes(x=period,y=1-reduction,group = scenario)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     geom_line(size = 0.5, aes(linetype=tgt2030, color = scenario, text = text)) + -->
<!--     #geom_point(size = 3, aes(shape = lim, fill = scenario, text = text)) + -->
<!--     #geom_line(data=h,size=0.5, color = "#000000") + -->
<!--     scale_linetype_manual(values = c("55"="twodash", "57"="solid", "59"="dashed"), guide = guide_legend(nrow =1, byrow = T, order = 1, override.aes = list(linewidth = 1.5))) +   scale_color_manual(values = scenarioColor, guide = guide_legend(nrow =4, byrow = T, order = 2, override.aes = list(linewidth = 1.5))) +  -->
<!--     scale_fill_manual(values = scenarioFill, guide = guide_legend(nrow =2, byrow = T, override.aes = list(shape = 21, size = 8), order = 3)) + -->
<!--     scale_shape_manual(values = c("default"=21,"limCCS"=22,"limH2"=23,"limVRE"=24), guide = guide_legend(nrow =2, byrow = T, order = 4, override.aes = list(size = 8))) + -->
<!--     theme_doubleColumn() + -->
<!--     theme(strip.text.y = element_blank()) + -->
<!--     #guides(fill = guide_legend(nrow = 2, byrow = T)) + -->
<!--     theme(legend.text=element_text(size=theme.single.text.size)) + -->
<!--     theme(legend.key.height = unit(0.7, "cm"), -->
<!--           legend.key.width = unit(2,"cm")) + -->
<!--     theme(legend.position="right", legend.direction = "vertical", legend.box = "vertical") +  -->
<!--     #theme(legend.key.width = unit(2,"cm")) + -->
<!--     theme(legend.spacing.y = unit(0.5, "lines")) +  -->
<!--     theme(legend.position = "none") + -->
<!--     scale_x_continuous(breaks = seq(1990,2060,10)) -->

<!--   g[["Emission reduction"]][["plotly"]] <- ggplotly(g[["Emission reduction"]][["ggplot"]],tooltip = c("text")) %>% layout(autosize = TRUE) -->

<!--   plotly2js( -->
<!--     g[["Emission reduction"]][["plotly"]], -->
<!--     div.id = "emission reduction", output.html = TRUE, output.file = "emission reduction.js",  -->
<!--     output.dir = jsOutputFolder, output.url = paste0(jsOutputFolder, "/emission reduction.html")) -->

<!-- ``` -->

<!-- ```{r, echo=FALSE, fig.width=8, fig.height=6} -->

<!--   g[["Emission reduction"]][["plotly"]] -->

<!-- ``` -->
